A survey of HTTP caching options on the open Web

### 2015-01-15 sanity/paper1.tex
An abstract
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@989 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
We have surveyed RDF resources on the Semantic Web for the use of HTTP
cache and conditional request headers. We find that while they are
prevalent enough to be used in some cases, they are not commonly used
even on relatively static data, and when they are given, they are very
conservatively set. We point out future directions and give
recommendations for the enhanced use of caching in the Semantic Web.
\end{abstract}
